---
title: '\ '
output: blogdown::html_page
params:
  seed: 1
editor_options: 
  chunk_output_type: inline
---

```{r, echo = F, message = F, warning = F}
# LS04 HISTOGRAMS DATA QUIZ

if(!require(pacman)) install.packages("pacman")
pacman::p_load(
  # necessary for all quizzes runs
  tidyverse, 
  here,
  knitr,
  googledrive,
  rio,
  #required for it to run:
  blogdown,
  shiny,
  readxl, 
  janitor,
  devtools,
  patchwork
  )
knitr::opts_chunk$set(warning = F, message = F)
source(here("global/functions/misc_functions.R"))
source(here("global/functions/ggplot_digest.R"))
# Setup for uploading images and datasets
if (!drive_has_token()) drive_auth(email = "trainingteam@thegraphnetwork.org")
options(gargle_oauth_email = "trainingteam@thegraphnetwork.org")
knitr::opts_knit$set(upload.fun = gdrive_upload) # pulled by knitr to upload image
# Set seed
set.seed(params$seed)
```

```{r echo = F}
# Prep data samples

diabetes_china <- 
  read_csv(here("data/raw/diabetes_china_chen.csv")) %>% 
  select(c(1:3, 5:14)) %>% 
  slice_sample(n = 200)

colnames(diabetes_china) <- c("id",
                              "age",
                              "sex",
                              "height_cm",
                              "weight_kg",
                              "bmi",
                              "sbp_mmHg",
                              "dbp_mmHg",
                              "fpg_mmol_L",
                              "cholesterol_mmol_L",
                              "triglyceride_mmol_L",
                              "hdl_mmol_L",
                              "ldl_mmol_L")

```

Welcome to your first data-based quiz on data visualization! For data-based quizzes, you will need to import data into R as you follow the questions.

```{r echo = F, results = "asis"}
upload_and_link(diabetes_china, filename = "diabetes_china", format =  "csv")
```

Note that each time you retry a quiz, the dataset is slightly modified so that you get a different set of countries.

# Diabetes dataset

Here, you will analyze parts of a dataset documenting clinical variables for 500 patients that were collected as part of a research study.

This version of the dataset contains a random sample of 200 records from the total 500. When you retake this quiz, you will get a different subset of the data.

Here are the top 6 rows of **`diabetes_china`** after import:

```{r}
head(diabetes_china)

```

Take a closer look at the composition of each of the 13 variable in this dataset:

```{r}
summary(diabetes_china)
```

In this quiz you will create histograms to look at the distribution of various numeric variables from this dataset.

**Complete the code below to create a histogram of BMI. Color the outline of the bars in `"coral"` and the inside in `"white"`.**

The resulting plot should look like this:

```{r echo = F}

ggplot(diabetes_china, aes(bmi)) +
  geom_histogram(color = "coral", fill = "white") +
  labs(x = "Body mass index (kg/m2)",
       y = "Count")
```

```{r eval = F}

ggplot({data} = diabetes_china, 
       mapping = aes(x = {bmi})) +
  {geom_histogram}(color = "coral",
                   fill = {"white"}) +
  {labs}({x} = "Body mass index (kg/m2)",
         y = {"Count"})
```

**Fill this code to add an aesthetic argument that will get rid of the warning message and result in a total of 9 bins.**

```{r echo=F}

ggplot(diabetes_china, aes(bmi)) +
  geom_histogram(color = "coral", 
                 fill = "white",
                 {[binwidth][bins]} = {[2][9]}) +
  labs(x = "Body mass index (kg/m2)",
       y = "Count")
```

```{r eval = F}

ggplot(diabetes_china, aes(bmi)) {+}
  geom_histogram({[color][col][colour]} = "coral", 
                 {fill} = {["#FFFFFF"]["white"]},
                 {binwidth} = 2)
```

The aesthetic argument we just added is a fixed aesthetic: {[true][t]} (**`true`** or **`false`**)

**Use the `diabetes_china`** **dataset in R to create a histogram of cholesterol levels.**

The plot should look like this:

```{r echo = F}
filled_bar <- ggplot(high_hiv_prev, aes(year, total_cases,
                          fill = country)) +
  geom_col()

filled_bar 
```