---
title: '\ '
output: blogdown::html_page
params:
  seed: 1
editor_options: 
  chunk_output_type: inline
---

```{r, echo = F, message = F, warning = F}
# LS06 BOSPLOTS DATA QUIZ

if(!require(pacman)) install.packages("pacman")
pacman::p_load(
  # necessary for all quizzes runs
  tidyverse, 
  here,
  knitr,
  googledrive,
  rio,
  #required for it to run:
  blogdown,
  shiny,
  readxl, 
  janitor,
  devtools,
  patchwork
  )
knitr::opts_chunk$set(warning = F, message = F)
source(here("global/functions/misc_functions.R"))
source(here("global/functions/ggplot_digest.R"))
# Setup for uploading images and datasets
if (!drive_has_token()) drive_auth(email = "trainingteam@thegraphnetwork.org")
options(gargle_oauth_email = "trainingteam@thegraphnetwork.org")
knitr::opts_knit$set(upload.fun = gdrive_upload) # pulled by knitr to upload image
# Set seed
set.seed(params$seed)
```

```{r echo = F}
# Prep data samples

nigerm <- 
  read_csv(here("data/clean/nigerm_cases_rgn.csv")) %>% 
  slice_sample(n = 2000)

```

Welcome to your first data-based quiz on data visualization! For data-based quizzes, you will need to import data into R as you follow the questions.

```{r echo = F, results = "asis"}
upload_and_link(nigerm, filename = "nigerm", format =  "csv")
```

Note that each time you retry a quiz, the dataset is slightly modified so that you get a different set of countries.

# Diabetes dataset

Here, you will analyze parts of a dataset documenting clinical variables for 500 patients that were collected as part of a research study.

Here are the top 6 rows of **`nigerm`** after import:

```{r}
head(nigerm)

```

Take a closer look at the composition of each of the 13 variable in this dataset:

```{r}
summary(nigerm)
```

This version of the dataset contains a random sample of 200 records from the total 500.

In this quiz you will create boxplots to look at the distribution of the `cases` numeric variable from `nigerm`, split by categorical variables such as `region` and `year`.

```{r message=FALSE, warning=FALSE, fig.width = 7, fig.height = 35}
theme_set(theme_grey())
nigerm05 <- nigerm %>% filter(!year == 2005)
a <- ggplot() +
  labs(title = "Layer 1")
b <- ggplot(nigerm05, aes(x = region, y = cases, fill = region)) +
  labs(title = "Layer 2")
c <- b + geom_boxplot(alpha = 0.8) + 
  labs(title = "Layer 3")
d <- c + facet_wrap(vars(year), ncol = 2) +
  labs(title = "Layer 4")
e <- d + stat_summary() +
  labs(title = "Layer 5")
f <- e + coord_cartesian(ylim = c(0, 2000)) +  
  scale_fill_brewer(palette = "Spectral") +
  labs(title = "Layer 6")
g <- f + theme_minimal(13) +
  labs(title = "Layer 7")
a + b + c + d + e + f + g + plot_layout(nrow = 7, ncol = 1)
```

