---
title: '\ '
output: blogdown::html_page
params:
  seed: 1
editor_options: 
  chunk_output_type: console
---

```{r, echo = F, message = F, warning = F}
if(!require(pacman)) install.packages("pacman")
pacman::p_load(
  # necessary for all quizzes runs
  tidyverse, 
  here,
  knitr,
  googledrive,
  rio,
  #required for it to run:
  blogdown,
  shiny,
  readxl, 
  janitor)
knitr::opts_chunk$set(warning = F, message = F)
source(here("global/functions/misc_functions.R"))
source(here("global/functions/ggplot_digest.R"))
# Setup for uploading images and datasets
if (!drive_has_token()) drive_auth(email = "trainingteam@thegraphnetwork.org")
options(gargle_oauth_email = "trainingteam@thegraphnetwork.org")
knitr::opts_knit$set(upload.fun = gdrive_upload) # pulled by knitr to upload image
# Set seed
set.seed(params$seed)
```

```{r echo = F}

high_hiv_prev_pop <- 
  read_csv(here("data/clean/high_hiv_prev_pop.csv"))

# Sample and plot
high_prev_countries <- high_hiv_prev_pop$country %>% unique()

high_prev_country_sample <- sample(high_prev_countries, 3)

high_hiv_prev <- high_hiv_prev_pop %>% 
  filter(country %in% high_prev_country_sample)

hiv_prevalence <- high_hiv_prev %>% 
  mutate(country = as.factor(country),
         year = as.factor(year))

# ggplot(high_hiv_prev, aes(year, total_cases,
#                           color = country)) +
#   geom_point()
# 
# ggplot(high_hiv_prev, aes(year, total_cases,
#                           color = country)) +
#   geom_line()
# 
# ggplot(high_hiv_prev, aes(year, total_cases,
#                           color = country)) +
#   geom_col()
# 
# ggplot(high_hiv_prev, aes(year, total_cases,
#                           fill = country)) +
#   geom_col()
```

Welcome to your first data-based quiz on data visualization! For data-based quizzes, you will need to import data into R as you follow the questions.

Note that each time you retry a quiz, the dataset is slightly modified.

# HIV dataset

Here, you will analyze parts of a dataset documenting global HIV prevalence from 1990 to 2011. 

```{r echo = F, results = "asis"}
upload_and_link(hiv_prevalence, filename = "hiv_prevalence", format =  "csv")
```

Here are the top 6 rows of `hiv_prevalence` after import:

```{r}
head(hiv_prevalence)
summary(hiv_prevalence)
```

**Complete the code below to create a scatter plot of HIV incidence over time.**

Hint: You plot should look like this:

```{r echo = F, fig.width=5}

ggplot(hiv_prevalence, aes(year, total_cases)) +
  geom_point()

```



```{r eval = F}

ggplot(data = {hiv_prevalence}, 
       {mapping} = aes({x} = year,
                       y = {total_cases})) {+}
  geom{_point}()
```

------------------------------------------------------------------------

Make this plot and save it as an R object:
```{r echo = F}
filled_bar <- ggplot(high_hiv_prev, aes(year, total_cases,
                          fill = country)) +
  geom_col()

filled_bar

hash <- ggplot_digest(filled_bar)
```

Put your plot object through the `ggplot_digest()` function and enter the resulting character string here: {`r hash`}
