---
title: 'Multiple-choice quiz | Line graphs'
output: blogdown::html_page
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: sentence
# quiz_title: '03.03 lines, scales, and labels'
# quiz_type: 'simple_theory'
# course_abbrev: 'IDAR'
---

```{r, echo = F, message = F, warning = F}
opts_chunk$set(warning = F, message = F)

if(!require(pacman)) install.packages("pacman")
pacman::p_load(tidyverse,
               googledrive,
               patchwork,
               rio,
               here,
               knitr)

# Setup for uploading images
source(here("global/functions/misc_functions.R"))
if (!drive_has_token()) drive_auth(email = "trainingteam@thegraphnetwork.org")
options(gargle_oauth_email = "trainingteam@thegraphnetwork.org")
knitr::opts_knit$set(upload.fun = gdrive_upload)

```

# Intro

This quiz tests your understanding of [lesson 3].
Good luck!

Quiz Contributors: [Zachary Anderson](https://thegraphcourses.org/members/zachary){target="_blank"}, [Joy Vaz](https://thegraphcourses.org/members/joy/){target="_blank"}, [Kene David Nwosu](https://thegraphcourses.org/members/kendavidn/){target="_blank"}

# Q - ??

What is the `geom_*()` function we use for line graphs?

## A

`geom_line()`

## B

`geom_linegraph()`

## C

`geom_scatter()`

## D

`geom_lines()`

## Answer

A

## Correct message

You have it all lined up!

`geom_line()` is used to create line graphs in {ggplot2}

## Incorrect message

That's a bit off.

`geom_line()` is used to create line graphs in {ggplot2}

# Q -

Line graphs, just like scatter plots, display the relationship between two numeric variables.

## A

TRUE

## B

FALSE

## Answer

A

## Correct message

It's all coming together!

As two-dimensional plots, line and scatter plots can both be used to show the relationship of two variables (if the variables are numbers.

## Incorrect message

As two-dimensional plots, line and scatter plots can both be used to show the relationship of two variables (if the variables are numbers.

# Q -

A line graph is an effective method of displaying relationships when one of the two variables represents time.
Therefore, it is preferred to use line graphs over scatter plots when the variable on the x-axis represents time.

## A

TRUE

## B

FALSE

## Answer

A

## Correct message

That's the one!

## Incorrect message

Please look at some of the examples about data across time from our lesson (or other sources).

# Q -

A line graph is an ineffective method of displaying relationships when one of the two variables represents time.
Therefore, it is preferred to use scatter plots over line graphs when the variable on the x-axis represents time.

## A

FALSE

## B

TRUE

## Answer

A

## Correct message

That's the one!

## Incorrect message

You might think that, but read the question again!
The examples about data across time from our lesson use line graphs, and you may find them in other sources as well.

# Q -

The `linetype` argument can be specified using a name (e.g., `“dotted”`) or with an integer.

## A

TRUE

## B

FALSE

## Answer

A

## Correct message

Specifically fit!
The `linetype` argument can be set with either integers or names from a select list.

## Incorrect message

Both are right!
The `linetype` argument can be set with either integers or names from a select list.

# Q -

Which of the following code blocks will produce a plot with a dotted line?

## A

Either `geom_line(linetype = "dotted")` or `geom_line(linetype = 3)`

## B

`geom_line(linetype = "dotted")`

## C

`geom_line(linetype = 3)`

## D

`geom_dotted_line()`

## Answer

A

## Correct message

Double plus good!
Both a specific list of integers and a specific list of names can be used with the `linetype` argument to make the line type of your choice.
(There is no `geom_dotted_line()`.)

```{r}
image
```

## Incorrect message

That was tricky!
Both a specific list of integers and a specific list of names can be used with the `linetype` argument to make the line type of your choice.
(There is no `geom_dotted_line()`.)

```{r}
image
```

# Q -

You can plot points on a line graph by adding a second `geom` layer using `geom_point()`

## A

TRUE

## B

FALSE

## Answer

A

## Correct message

You got it together!
Try out the following graph as an example:

```{r}
ggplot(data = beaver1, 
       mapping = aes(x = time, y = temp)) + 
  geom_line() + 
  geom_point()
```

## Incorrect message

Please go back and find where this was shown in the lesson.
You can also try out the following graph as an example:

```{r}
ggplot(data = beaver1, 
       mapping = aes(x = time, y = temp)) + 
  geom_line() + 
  geom_point()
```

# Q -

A plot must have one and only one `geom_*` layer.

## A

FALSE

## B

TRUE

## Answer

A

## Correct message

You're number one!
However, the geom plots aren't.
As long as the plots are compatible, you can layer them together.
This may be especially useful for illustrating specific points of interest about your data.

```{r}

```

## Incorrect message

Let's bring it together.
As long as the plots are compatible, you can layer them.
This is especially useful for illustrating specific points of interest about your data.

```{r}

```

# Q -

The linetype argument can only be used as a fixed aesthetic, not an aesthetic mapping.

## A

FALSE

## B

TRUE

## Answer

A

## Correct message

Keeping it in line!

`linetype` can be applied to both aesthetic mapping and fixed aesthetic.

```{r}

```

## Incorrect message

`linetype` can be applied to both aesthetic mapping and fixed aesthetic.

```{r}

```

# Q -

The `linetype` argument can only be used as an aesthetic mapping, not a fixed aesthetic.

## A

FALSE

## B

TRUE

## Answer

A

## Correct message

You have the right type!
`linetype` can be applied to both aesthetic mapping and fixed aesthetic.

```{r}

```

## Incorrect message

`linetype` can be applied to both aesthetic mapping and fixed aesthetic.

```{r}

```

# Q - seq for scale breaks

{ggplot2} automatically scales aesthetic mappings like x and y position.

For example, here the x axis is divided into 5-year intervals.

```{r}
# Subset population dataset from tidyr to data from one country
afg_pop <- tidyr::population %>% filter(country == "Afghanistan")
head(afg_pop)

# Plot line graph of population by year
ggplot(data = afg_pop, 
       mapping = aes(x = year, y = population)) +
  geom_line()
```

We can control position of scale break of continuous x & y axes with `scale_*_countinuos`.

Which function can we use to make a numeric vector for scale breaks?

## A

`seq()` or `c()`

## B

`seq()`

## C

`sequence()`

## D

`unique()`

## E

`c()`

## Answer

A

## Correct message

Good job breaking it down!

Both `seq()` and `c()` can make a numeric vector.
For example, these two code chunks achieve the same result:

```{r}
# Manually type vector
c(1995, 1998, 2001, 2004, 2007, 2010, 2013)

# Generate a sequence with regular intervals
seq(1995, 2013, 3)
```

However we recommend `seq()` as it is faster and will ensure your scale breaks are evenly spaced.

## Incorrect answer

Both `seq()` and `c()` can make a numeric vector.
For example, these two code chunks achieve the same result:

```{r}
# Manually type vector
c(1995, 1998, 2001, 2004, 2007, 2010, 2013)

# Generate a sequence with regular intervals
seq(1995, 2013, 3)
```

However, we recommend `seq()` as it is faster and will ensure your scale breaks are evenly spaced.

```{r}
# Add scales layer and by give a numeric vector of positions to the `breaks` argument
ggplot(data = afg_pop, 
       mapping = aes(x = year, y = population)) +
  geom_line() +
  scale_x_continuous(breaks = seq(1995, 2013, 3))
```

# Q

The code below attempts to visualize and compare trends of GDP per capita over time for countries in West Africa.

However, the resulting plot doesn't allow us to tell the countries apart.

```{r}
pacman::p_load(gapminder)

gap_wafr <- gapminder::gapminder %>% 
  filter(country %in% c("Nigeria", "Ghana", "Guinea", "Senegal"))

ggplot(data = gap_wafr, 
       mapping = aes(y = gdpPercap, x = year)) +
  geom_line() +
  geom_point()
```

What aesthetic can you add in order to visualize *and* compare trends between countries?

Hint: Use the `gapminder` package and try these options out in R

## A

`color = country` as a fixed aesthetic

## B

`color = continent` as an aesthetic mapping

## C

`fill = country` as an aesthetic mapping

## D

`group = country` as fixed aesthetic

## E

None of these options will produce the desired result.

## Answer

E

## Correct message

Good thinking!

If you try these different options in R, you will see that none of these options will create a plot which tells you which line belongs to which country.
Some of them might separate the lines, but there won't be any visual indication of which one belongs to which country.

-    `color = country` as a fixed aesthetic will give you an error.
    This would work as a *mapping*, but not a fixed aesthetic.
    Fixed aesthetics are set to constant value that doesn't vary with the data.

    ```{r}
    # Fix color to country (error)
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year)) +
      geom_line(color = country) +
      geom_point()

    # Fix color to a color (incorrect)
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year)) +
      geom_line(color = "forestgreen") +
      geom_point(color = "red")


    # Map color to country (correct)
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year, color = country)) +
      geom_line() +
      geom_point()
    ```

-   `fill = country` will separate the data because it's trying to give a separate fill color to each country, but all the lines and points will stay black.
    These geoms won't respond to the `fill` argument because neither of them have an *interior* for fill color.

    ```{r}
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year, fill = country)) +
      geom_line() +
      geom_point()
    ```

-   `group = country` will separate the lines, but again they will all be the same color

    ```{r}
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year, group = country)) +
      geom_line() +
      geom_point()
    ```

-   `color = continent` will not help either

    ```{r}
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year, color = continent)) +
      geom_line() +
      geom_point()
    ```

Point color be changed with `fill` if `shape` is assigned to a fillable shape.

```{r}
ggplot(data = gap_wafr, 
       mapping = aes(y = gdpPercap, x = year, fill = country)) +
  geom_line() +
  geom_point(shape = 23)
```

## Incorrect message

If you try these different options in R, you will see that none of these options will create a plot which tells you which line belongs to which country.
Some of them might separate the lines, but there won't be any visual indication of which one belongs to which country.

-    `color = country` as a fixed aesthetic will give you an error.
    This would work as a *mapping*, but not a fixed aesthetic.
    Fixed aesthetics are set to constant value that doesn't vary with the data.

    ```{r}
    # Fix color to country (error)
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year)) +
      geom_line(color = country) +
      geom_point()

    # Fix color to a color (incorrect)
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year)) +
      geom_line(color = "forestgreen") +
      geom_point(color = "red")


    # Map color to country (correct)
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year, color = country)) +
      geom_line() +
      geom_point()
    ```

-   `fill = country` will separate the data because it's trying to give a separate fill color to each country, but all the lines and points will stay black.
    These geoms won't respond to the `fill` argument because neither of them have an *interior* for fill color.

    ```{r}
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year, fill = country)) +
      geom_line() +
      geom_point()
    ```

-   `group = country` will separate the lines, but again they will all be the same color

    ```{r}
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year, group = country)) +
      geom_line() +
      geom_point()
    ```

-   `color = continent` will not help either

    ```{r}
    ggplot(data = gap_wafr, 
           mapping = aes(y = gdpPercap, x = year, color = continent)) +
      geom_line() +
      geom_point()
    ```

Point color be changed with `fill` if `shape` is assigned to a fillable shape.

```{r}
ggplot(data = gap_wafr, 
       mapping = aes(y = gdpPercap, x = year, fill = country)) +
  geom_line() +
  geom_point(shape = 23)
```

# Q 

Which of these {ggplot2} functions work for transform axis scaling from linear to logarithmic?

## A

`scale_x_log()`

## B

`scale_x_log10()`

## C

`scale_x_continuous()`

## D

`scale_log_x()`

## Answer

B

## Correct message

## Incorrect message

# Q 

Which of these {ggplot2} functions work for transform axis scaling from linear to logarithmic?

## A

`scale_y_ln()`

## B

`scale_y_log10()`

## C

`scale_y_continuous()`

## D

`scale_log10_y()`

## Answer

B

## Correct message

Great memory!

It's ease to get these mixed up.
Note that {ggplot2} scale functions start with `scale_*` where `*` is the name of the aesthetic mapping being scaled.
There are many scale functions like `scale_fill_*()`, `scale_color_*()`, `scale_alpha_*()`, `scale_size_*()`, etc. that give you fine control of each aesthetic mapping.

## Incorrect message

It's ease to get these mixed up.
Note that {ggplot2} scale functions start with `scale_*` where `*` is the name of the aesthetic mapping being scaled.
There are many scale functions like `scale_fill_*()`, `scale_color_*()`, `scale_alpha_*()`, `scale_size_*()`, etc. that give you fine control of each aesthetic mapping.
