



# Q 26: 

The following code chunk generates a scatterplot of age and the daily number of TV hours watched, from a survey in the US:

```{r}
survey_sample <- forcats::gss_cat %>% slice_sample(n = 200) # sample 100 respondents
head(survey_sample)

ggplot(survey_sample, 
       aes(x = age, y = tvhours)) + 
  geom_point()
```

Which of the following would apply an aesthetic mapping to differentiate by the `marital` variable?

## A

```{r eval = F}
ggplot(survey_sample,
       aes(x = age, y = tvhours)) + 
  geom_point(color = marital)
```

## B

```{r eval = F}
ggplot(survey_sample,
       aes(x = age, y = tvhours)) + 
  geom_point_colored(color = marital)
```

## C

```{r eval = F}
ggplot(survey_sample,
       aes(x = age, y = tvhours, color = marital)) + 
  geom_point()
```

## D

```{r eval = F}
ggplot(survey_sample,
       aes(x = age, y = bmi)) + 
  geom_point(sex = c(male = "blue", female = "orange"))
```

## Answer

C

## Correct message

You got it!

`color = marital` inside the `aes` mapping will produce different colors for each marital status. The other three code chunks don't work.

Here is the final plot:

```{r}
ggplot(survey_sample,
       aes(x = age, y = tvhours, color = marital)) + 
  geom_point()
```

The {forcats} package is part of the tidyverse, so you should be able to work with this data on your own computer

## Incorrect message

`color = marital` inside the `aes` mapping will produce different colors for each marital status. The other three code chunks don't work.

Here is the final plot:

```{r}
ggplot(survey_sample,
       aes(x = age, y = tvhours, color = marital)) + 
  geom_point()
```

The {forcats} package is part of the tidyverse, so you should be able to work with this data on your own computer



  