---
title: '\ '
output: blogdown::html_page
editor_options: 
  chunk_output_type: console
quiz_title: '03.03 ggplot() basics'
quiz_type: 'simple_theory'
course_abbrev: 'IDAR'
---

```{r, echo = F, message = F, warning = F}
if(!require(pacman)) install.packages("pacman")
pacman::p_load(tidyverse, 
               here,
               googledrive,
               knitr)

source(here("global/functions/misc_functions.R"))

# Setup for uploading images
if (!drive_has_token()) drive_auth(email = "trainingteam@thegraphnetwork.org")
options(gargle_oauth_email = "trainingteam@thegraphnetwork.org")
knitr::opts_knit$set(upload.fun = gdrive_upload) # pulled by knitr to upload image

opts_chunk$set(warning = F, message = F)
```




## Prologue

This quiz tests your understanding of the basic functioning of the {ggplot2} package. Good luck!
  
For multiple choice questions, please enter the correct letter option into the provided box.

------------------------------------------------------------------------

# Q1:

What does the `gg` in `ggplot2` stand for?

## A

good game

## B

grey goose

## C

grammar of graphics

## D

Ghanaian gentleman

## Answer

C

## Correct message

Good game!
GG stands for **G**rammar of **G**raphics.

## Incorrect message

Nice try, but not this time.
GG stands for **G**rammar of **G**raphics.

------------------------------------------------------------------------

# Q2: 

What is the name of the R package that we will use for data visualization?

## A

{base}

## B

{ggplot}

## C

{tidyverse}

## D

{ggplot2}

## Answer

D

## Correct message

You remembered! We use {ggplot2} for this course.

## Incorrect message

Sorry, that's not it. If you go back to the lessons, or some of the Esquisser graphs we've made, you'll see we use {ggplot2}.

------------------------------------------------------------------------
# Q3:

True or False: The {ggplot2} package is part of the {tidyverse} meta-package.

## A

FALSE

## B

TRUE

## Answer

B

## Correct message

It is indeed!

## Incorrect message

We've used several useful functions from {tidyverse}, and {ggplot2} is in there too.

------------------------------------------------------------------------
# Q4: 

True or False: The `ggplot2` package is part of the base R installation and does not require to be loaded before its use.

## A

FALSE

## B

TRUE

## Answer

A

## Correct message

Great going! We've had to load {ggplot2} whenever we use it.

## Incorrect message

If you try to use {ggplot2} without loading it, you'll definitely get an error message!

------------------------------------------------------------------------
# Q5: 

Which of the code segments below will NOT work to load the {ggplot2} package?

## A

`{r eval = F} library(tidyverse)`

## B

`{r eval = F} library(ggplot)`

## C

`{r eval = F} library(ggplot2)`

## Answer

B

## Correct message

**G**ood **g**ame! Loading either {ggplot2} or {tidyverse} (which includes {ggplot2}) get us {ggplot2}.

## Incorrect message

Look carefully! {ggplot} is not the same thing as {ggplot2}.

------------------------------------------------------------------------
# Q6:

True or False: When you plot with 'ggplot2' you have to follow a certain grammar to build up your plots.

## A

TRUE

## B

FALSE

## Answer

A

## Correct message

It's the **g**rammar of **g**raphics that we're learning right now!

## Incorrect message

It's the **g**rammar of **g**raphics that we're learning right now!

------------------------------------------------------------------------
# Q7: 

True or False: The `ggplot` function requires all 7 layers to be defined.

## A

FALSE

## B

TRUE

## Answer

A

## Correct message

Correct! Only three layers are necessary for it to work.

## Incorrect message

If you go back through the lesson, you'll see that we've made several plots with only three layers.

------------------------------------------------------------------------
# Q8: 

What are the three essential layers for the `ggplot` function?

## A

Facets, Data, and Statistics

## B

Coordinates, Data, and Themes

## C

Data, Geometries, and Aesthetics

## Answer

C

## Correct message

You're **g**oing for the **g**old!
We need Data, Geometries, and Aesthetics for `ggplot` to work.

## Incorrect message

We need Data, Geometries, and Aesthetics for `ggplot` to work.
Go back to the lesson and see!
  
------------------------------------------------------------------------
# Q9: 

What do we provide in the `data` layer?

## A

the dataset containing the variables of interest

## B

the date a plot was created

## C

the data formation of the final plot

## Answer

A

## Correct message

That's right! 

## Incorrect message

We need a set of data to have something to graph.

------------------------------------------------------------------------
# Q10:

What do we provide in the `geom` layer?

## A

the geometrical coordinates

## B

the colors that we want to use for the plotting

## C

the types of geometric objects to plot

## D

grades from geometry class

## Answer

C

## Correct message

Splendid!
The coordinates are worked out by the `data`, and the color is an `aes`thetic concern, but the objects belong to the `geom`etry layer.

## Incorrect message

Try again!
The coordinates are worked out by the `data`, and the color is an `aes`thetic concern, but the objects belong to the `geom`etry layer.

------------------------------------------------------------------------
# Q11: 

What do we provide in the `aes` layer?

## A

the aesthetic attributes of the geometric objects

## B

the aes standard that we want to use for plotting

## C

**A**ll the **E**ssential **S**tatistical information

## Answer

A

## Correct message

Looks like you got it!
The `aes` layer defines the plots' `aes`thetics.

## Incorrect message

The `aes` layer defines the plots' `aes`thetics.

------------------------------------------------------------------------
# Q12:

In which layer would you define the color of your geometric object as an aesthetic mapping?

## A

the `aes` layer

## B

the `geom` layer

## C

the `facets` layer

## D

the `data` layer

## Answer

A

## Correct message

Exactly right!
It's defined with the `aes`thetic layer.

## Incorrect message

Sorry, that's not it!
It's defined with the `aes`thetic layer.

------------------------------------------------------------------------
# Q13:

In which layer would you define the color of your geometric object as a fixed aesthetic?

## A

the `aes` layer

## B

the `geom` layer

## C

the `facets` layer

## D

the `data` layer

## Answer

A

## Correct message

Far out!
It's defined with the `aes`thetic layer.

## Incorrect message

Look again!
It's defined with the `aes`thetic layer.

------------------------------------------------------------------------
# Q14:

True or False: A big advantage of {ggplot2} and its syntax is that it is very flexible and allows for a high degree of customization.

## A

FALSE

## B

TRUE

## Answer

B

## Correct message

That's it!

## Incorrect message

That's not it.

------------------------------------------------------------------------
# Q15:

True or False: To add more layers to a plot, you have to nest the different functions of `ggplot()`.

## A

TRUE

## B

FALSE

## Answer

B

## Correct message

As we've seen, `ggplot()` functions can be added incrementally.

## Incorrect message

As we've seen, `ggplot()` functions can be added incrementally.

------------------------------------------------------------------------
# Q16:

True or False: A statistical graphic is a `mapping` of `data` variables to `aes`thetic attributes of `geom`etric objects.

## A

TRUE

## B

FALSE

## Answer

A

## Correct message

Indeed!

## Incorrect message

Sorry.

------------------------------------------------------------------------
# Q17:

How many layers are in the **G**rammar of **G**raphics framework, and how many of them are required for a complete plot?

## A

There are 5 layers in total with 2 required ones.

## B

There are 7 layers in total with 3 required ones.

## C

There are 3 layers in total and all of them are required.

## Answer

B

## Correct message

**G**reat **g**oing! {ggplot2} has 7 layers, of which 3 are absolutely necessary to function.

## Incorrect message

{ggplot2} has 7 layers, of which 3 are absolutely necessary to function.

------------------------------------------------------------------------
# Q18:

The first layer in `ggplot()` is the data layer. Select the code block below that defines this layer.

## A

```{r eval = F}
ggplot(data=dengue)
```

## B

```{r eval = F}
ggplot() + data(dengue)
```

## C

```{r eval = F}
ggplot.data(dengue)
```

## Answer

A

## Correct message

That's the one!

## Incorrect message

If you look at the code from the lesson, you can see how we define data for `ggplot()`

------------------------------------------------------------------------
# Q19:

In which layer do we add the visual properties of `ggplot2()`?

## A

`data`

## B

`mapping`

## C

`aes`

## D

`geom`

## Answer

C

## Correct message

The `aes`thetic layer sets how the visual properties are applied to the `geom`etric layer.

## Incorrect message

The `aes`thetic layer sets how the visual properties are applied to the `geom`etric layer.

------------------------------------------------------------------------
# Q20:

You study how the weight of individuals in your study group is related to their height. For this you want to do a plot with the `weight` variable on the y-axis, the `height` variable on the x-axis and your dataset is called `participants`.
Which of the codes below will create this plot?

## A

```{r eval = F}
ggplot(data = participants) +
       mapping = aes(x = height, 
           y = weight)
```

## B

```{r eval = F}
ggplot(data = participants,
       x = height, 
       y = weight)
```

## C

```{r eval = F}
ggplot(data= participants, 
       mapping = aes(x = height + 
           y = weight)) +
  geom_point()
```

## D

```{r eval = F}
ggplot(data= participants, 
       mapping = aes(x = height, 
           y = weight)) +
  geom_point()
```

## Answer

D

## Correct message



## Incorrect message



------------------------------------------------------------------------
# Q21:

You plot your graph with the following code:
  
```{r eval = F}
ggplot(data= participants,
  mapping = aes(x = height, y = weight))
```

When you execute the code, you see a graph with the right variables on each axis, however, you do not see and data that is on the plot. Why are there no visible data points?

## A

No color has been defined for the plot, so all the data points are transparent.

## B

No geometric layer has been defined yet.

## C

Your dataset it probably empty, so there's nothing to plot.

## D

The plot color is the same as the background color.

## Answer

B

## Correct message

**G**ood **g**ame! We still need a geometric layer.

## Incorrect message

Look closer. We still need a geometric layer.

------------------------------------------------------------------------
# Q22:

True or False: Geometric objects are defined in the `geom` layer. Such layers are added with functions that start with `geom_`.

## A

TRUE

## B

FALSE

## Answer

A

## Correct message

That's the one!

## Incorrect message


------------------------------------------------------------------------
# Q23: 

Which of the below functions is not a `geom_*()` function in {ggplot2}?

## A

point()

## B

geom_point()

## C

geom_line()

## D

geom_bar()

## Answer

A

## Correct message

**G**reat **g**oing!

## Incorrect message

That's actually a valid function. Look them up!

------------------------------------------------------------------------
  
# Q24:

What is an `aes`thetic mapping?

## A

the application of specific colors, shapes, etc. to separate aspects of a plot

## B

a legend that identifies which variables are shown by which colors, shapes, etc.

## C

the application of a given `aes`thetic to **all** the figures in a plot

## D

the layer showing colors, shapes, etc.

## Answer

A

## Correct message

Nice work!
If you want different `aes`thetic choices to be used in different parts of a plot, you can use an `aes`thetic mapping inside the `aes()` function.

## Incorrect message

That was a tricky one!
If you want different `aes`thetic choices to be used in different parts of a plot, you can use an `aes`thetic mapping inside the `aes()` function.

------------------------------------------------------------------------

# Q25: 

Which of the following would you use to make **all** the points in a graph larger?

## A

aesthetic mapping

## B

statistic layering

## C

vector multiplication

## D

a fixed aesthetic

## Answer

D

## Correct message

A fixed `aes`thetic applies to all the figures in a graph.

## Incorrect message

A fixed `aes`thetic applies to all the figures in a graph.

------------------------------------------------------------------------

# Q26: 

Given the following code chunk,

```{r eval = F}
ggplot(data= health_charts,
  mapping = aes(x = age, y = bmi))
+ geom_point()
```

which of the following would apply an aesthetic mapping to differentiate by sex?

## A

```{r eval = F}
ggplot(data= health_charts,
  mapping = aes(x = age, y = bmi))
+ geom_point(color = sex)
```

## B

```{r eval = F}
ggplot(data= health_charts,
  mapping = aes(x = age, y = bmi, z = sex))
+ geom_point()
```

## C

```{r eval = F}
ggplot(data= health_charts,
  mapping = aes(x = age, y = bmi, color = sex))
+ geom_point()
```

## D

```{r eval = F}
ggplot(data= health_charts,
  mapping = aes(x = age, y = bmi))
+ geom_point(sex c(male = "blue", female = "orange"))
```

## Answer

C

## Correct message

You got it!
`color = sex` inside the `aes` mapping will produce different colors for each sex. The other three code chunks don't work.

## Incorrect message

`color = sex` inside the `aes` mapping will produce different colors for each sex. The other three code chunks don't work.

------------------------------------------------------------------------

# Q27: 

Many programmers start off building a small chunk of code, testing to see if it works, and adding a bit more, seeing if it works, and building the program one step at a time.
What's the name for this process?

## A

incremental composition

## B

pyramid steps

## C

candle dipping

## D

layered development

## Answer

A

## Correct message

You got it!

## Incorrect message

That wasn't the right name. But really, the important idea is the **process**.

------------------------------------------------------------------------

# Q28: 

This lesson recommended we put each new element on a separate line. In fact, it's good practice to make **all** our code legible, not just when using `ggplot()`.
But *why* do we want legible code?

## A

If we're showing our code to someone else, it should be easy for them to read.

## B

Trick question, we don't! It's better to keep our code hidden to confuse our enemies.

## C

If we need to come back and change our code, or debug it, this makes the different parts easier to see.

## D

We want legible code for both our own sake as well as anyone else reading it.

## Answer

D

## Correct message

As we learned in team exercises, legible code is important for others to read.
And as we learned in reviewing our own code, seeing the pieces separately makes it easier to understand how they fit together.

## Incorrect message

As we learned in team exercises, legible code is important for others to read.
And as we learned in reviewing our own code, seeing the pieces separately makes it easier to understand how they fit together.
